---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
body {
  font-family: Arial, sans-serif;
}

h2 {
  color: #2c3e50;
}

p {
  font-size: 16px;
}
```


## Analysis of My YouTube Channel Videos

This dynamic report tracks videos uploaded on my YouTube channel.
It explores the video length, video type, thumbnail style, and view counts of my videos.

```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRkTa6aNQoSCO0K4k09MklEJsfwABqqwqCaCcmmmkJS17FYiNRI3EY33LRvvTI6n2do0NVX8PHcLbg-/pub?output=csv")

latest_data <- tibble(
  Timestamp = logged_data[[1]],
  length_minutes = as.numeric(logged_data[[2]]),
  video_type = as.character(logged_data[[3]]),
  thumbnail_face = as.character(logged_data[[4]]),
  views = as.numeric(logged_data[[5]])
)
mean_length <- mean(latest_data$length_minutes, na.rm = TRUE)
mean_views <- mean(latest_data$views, na.rm = TRUE)
most_views <- max(latest_data$views, na.rm = TRUE)
video_count <- length(latest_data$length_minutes)
```
I analysed `r video_count` videos from my YouTube channel.

The average video length is `r round(mean_length, 1)` minutes.

The average number of views is `r round(mean_views, 1)` views.

The highest number of views in this dataset is `r most_views` views.

```{r}
video_type_counts <- latest_data |>
  count(video_type)

ggplot(video_type_counts, aes(x = video_type, y = n)) +
  geom_col() +
  labs(
    title = "Distribution of Video Types",
    x = "Video Type",
    y = "Number of Videos"
  )
```
```{r}
thumbnail_face_counts <- latest_data |>
  count(thumbnail_face)

ggplot(thumbnail_face_counts, aes(x = thumbnail_face, y = n)) +
  geom_col() +
  labs(
    title = "Thumbnail Face Appearance",
    x = "Face in Thumbnail",
    y = "Number of Videos"
  )
```



